---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  out.width = "100%"
)

library(knitr)
```

# Files for plotting maps of Canada

This repository contains **simplified** GeoJSON and shapefiles for plotting maps of Canada. The original shapefiles were obtained from [Statistics Canada 2016 Census - Boundary files](https://www12.statcan.gc.ca/census-recensement/2011/geo/bound-limit/bound-limit-2016-eng.cfm) which are saved in the [`statcan_files/`](statcan_files/) directory.

The purpose of this repository is to provide simplified map files, as the original files can be large and takes time to plot. **The simplifying process can remove fine details in the boundaries, especially along small geographies**.


## What to download

The converted files are available in the [`exported_files`](exported_files/) directory as  
- GeoJSON files obtained from directly converting shapefiles ([`province_territory.geojson`](exported_files/province_territory.geojson)),  
- GeoJSON files of the simplified boundaries ([`province_territory_simplified.geojson`](exported_files/province_territory_simplified.geojson)),  
- shapefiles of the simplified boundaries ([`province_territory_simplified_sp`](exported_files/province_territory_simplified_sp/)).  


## Example: How to plot in `R`

These are plotted using the [`ggplot2`](https://ggplot2.tidyverse.org/) package. See [1] and [2] for code to plot using base plotting functions.

```{r library_import}

library(ggplot2)

```

### From shapefiles

```{r shapefile_plot}

province_territory_map_sim_sp <- rgdal::readOGR(dsn = here::here("exported_files", "province_territory_simplified_sp"), 
                                                layer = "province_territory_simplified_sp",
                                                use_iconv = TRUE)

ggplot(data = province_territory_map_sim_sp,
       mapping = aes(x = long, y = lat, group = group)) + 
  geom_polygon(colour = "white") + 
  theme_void()

```

### From GeoJSON files

```{r geojson_plot}

province_territory_map_sim_json <- geojsonio::geojson_read(here::here("exported_files", "province_territory_simplified.geojson"),
                                                           what = "sp")

ggplot(data = province_territory_map_sim_json,
       mapping = aes(x = long, y = lat, group = group)) + 
  geom_polygon(colour = "white") + 
  theme_void()

```



## Additional notes

The R code used to generate simplified boundary files are available at [`r_src/generate_geojson.r`](r_src/generate_geojson.r).



## References

[1] [https://www.r-graph-gallery.com/168-load-a-shape-file-into-r.html](https://www.r-graph-gallery.com/168-load-a-shape-file-into-r.html)  
[2] [https://www.r-graph-gallery.com/325-background-map-from-geojson-format-in-r.html](https://www.r-graph-gallery.com/325-background-map-from-geojson-format-in-r.html)  
